Cryptographic assurance of secrecy and fairness in voting

### 2012-12-07 paper/paper.tex
More pret-a

Upon arriving at the polling place, a voter receives one or more ballots. She chooses one of her ballots forms at random and privately marks her vote on the right-hand side. She detaches her cast vote from the corresponding candidate list on the left-hand side, which is subsequently destroyed. Her cast vote is scanned into and recorded by the system, which prints a digital signature on the now recorded ballot to constitute a receipt. The voter retains this receipt to later verify that her vote appears correctly in the tally.

The voter can optionally request an audit of her other ballot(s) to test that the decrypted onion on the right-hand side in fact corresponds to the ordering of candidates printed on the left-hand side. Once audited, a ballot can no longer be cast. Independent auditing authorities may also randomly choose uncast ballots to audit throughout the election process to provide further assurance.

>>>>

Upon arriving at the polling place, a voter receives one or more ballots. She chooses one of her ballot forms at random and privately marks her vote on the right-hand side. She detaches her cast vote from the corresponding candidate list on the left-hand side, which is subsequently destroyed. Her cast vote is scanned into and recorded by the system, which prints a digital signature on the now recorded ballot to constitute a receipt. The voter retains this receipt to later verify that her vote appears correctly in the tally.

The voter can optionally request an audit of her other, unused ballots to test that the decrypted onion on the right-hand side in fact corresponds to the ordering of candidates printed on the left-hand side. Since she arbitrarily chose which ballot to actually cast, this process offers assurance that it too is correct. Once audited, a ballot can no longer be cast. Independent auditing authorities may also randomly choose uncast ballots to audit throughout the election process to provide further assurance.
